1-methods-toys

### 2017-10-03 analysis/analyses/evaluate_toy/1-methods-toys.Rmd
added method qc, moved analyses in separate folders
updated toy params

```{r}
library(tidyverse)
library(dyneval)

@@

tasks <- generate_toy_datasets()
tasks <- tasks[1, ]
```

We choose certain parameters for which we know that the method will find (or focus on finding) a linear trajectory, and will do this quickly
```{r}
method_params <- yaml::yaml.load_file("conf/toy_params.yml")$linear
method_names <- names(method_params)
# method_names <- c("ouija", "slice")

>>>>

```{r}
library(tidyverse)
library(dyntoy)
library(dyneval)

@@

tasks <- generate_toy_datasets(num_cells=500)
#tasks <- tasks[1, ]
```

```{r}
task <- dynutils::extract_row_to_list(tasks, 2)
pheatmap::pheatmap(task$counts)
```

We choose certain parameters for which we know that the method will find (or focus on finding) a linear trajectory, and will do this quickly
```{r}
method_params <- yaml::yaml.load_file("toy_params.yml")$linear
method_names <- names(method_params)
# method_names <- c("ouija", "slice")
